\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[b4paper]{geometry}
\geometry{margin=0.5in}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

% Commands for my Contact Information
\newcommand{\fullname}{Massimo Caruso}
\newcommand{\phone}{(514) 944-5977}
\newcommand{\email}{massimo02caruso@gmail.com}
\newcommand{\linkedin}{linkedin.com/in/massimocaruso}
\newcommand{\github}{github.com/Extinctable}

% Commands for Recipient Information
\newcommand*{\hiringManager}{Hiring manager}
\newcommand*{\company}{COMPANY}
\newcommand*{\address}{STREETNUMBER STREETNAME, CITY, PROVINCE POSTALCODE}

%Commands for the Body Paragraphs
\newcommand*{\position}{POSITION}
\newcommand*{\companyDetails}{COMPANYDETAILS}
\newcommand*{\positionDetails}{POSITIONDETAILS}

% Name and Contact Information
\begin{center}
    {\Huge \textbf{\fullname}} \\
    \vspace{1mm}
    {\small 
    \faPhone \hspace{0mm} \href{tel:+15149445977}{\phone} $\vert$ 
    \faEnvelope \hspace{0mm} \href{mailto:massimo02caruso@gmail.com}{\email} $\vert$ 
    \faLinkedin \hspace{0mm} \href{https://linkedin.com/in/massimocaruso}{\linkedin} $\vert$ 
    \faGithub \hspace{0mm} \href{https://github.com/Extinctable}{\github}
    }
\end{center}

% Recipient Information
\vspace{1.5em}
\hiringManager \hfill \today \\
\company \\
\address 


% Opening
\vspace{1.5em}
Dear \hiringManager,

I am thrilled to apply for the \position \space role at \company. As a fourth year Software Engineering student at Concordia University, I bring a robust foundation in software development, coupled with hands-on experience from academic and professional projects.

% Body

% PayFacto description
During my internship at PayFacto, I worked on the deployment and implementation of MEVWeb, a province-wide cloud-based SaaS platform mandated by Revenu Québec. I supported the acquisition, cleaning, and preprocessing of merchant data to ensure accurate system onboarding and compliance. I also participated in end-to-end software deployments, both remotely and on-site, including planning, testing, and installation, and contributed to validating software builds by testing deployment packages and reporting bugs prior to production rollout. This experience strengthened my understanding of real-world SaaS deployment, cross-functional collaboration, and the operational considerations required when delivering compliant, production-ready software.

% Hexploit Alliance / AtHackCTF description
As a challenge designer with the Hexploit Alliance at \href{https://www.athackctf.com}{AtHackCTF}, I designed a security challenge simulating an access control system using MIFARE Classic cards, focusing on vulnerabilities like weak key management and privilege escalation. Participants reverse-engineered RFID memory sectors and forged admin access, gaining hands-on experience with embedded systems security.

As part of the AtHackCTF 2025 organizing team, I prepared over 600 MIFARE Classic cards by writing custom data, ensuring proper formatting and labeling, and supporting event logistics. I also coordinated the distribution of RFID card readers and facilitated a lockpicking activity, contributing to a hands-on learning environment focused on practical security concepts.

% Academic Projects
In addition, my academic projects strengthened my applied software and systems engineering skills. I designed and implemented a secure wireless access control system using ESP32 microcontrollers with BLE and LoRa communication, incorporating multi-factor authentication, encrypted alert messaging, tamper detection, and actuator-based lock control. This project emphasized embedded firmware development, state-machine design, and secure communication between distributed nodes. I also developed an online Food Database System, where I worked with APIs and relational databases to manage data ingestion, querying, and user interactions, reinforcing my experience with Python, JavaScript, SQL, and end-to-end application development.

% Why This Company
What excites me most about \company \space is \companyDetails. I am particularly drawn to the opportunity to \positionDetails.

% Closing
I am confident that my technical skills, academic achievements, and passion for software engineering make me a strong candidate for the \position \space role. I would welcome the opportunity to discuss how my experiences align with the needs of your team. Please feel free to reach out to me at \href{tel:+15149445977}{\phone} or \href{mailto:\email}{\email}.

\vspace{1.5em}
Thank you for considering my application. I look forward to the possibility of contributing to \company's success.

% Signoff
\vspace{2em}
Sincerely, \\
\fullname

\newpage

% Name and Contact Information
\begin{center}
    {\Huge \textbf{\fullname}} \\
    \vspace{1mm}
    {\small 
    \faPhone \hspace{0mm} \href{tel:+15149445977}{\phone} $\vert$ 
    \faEnvelope \hspace{0mm} \href{mailto:massimo02caruso@gmail.com}{\email} $\vert$ 
    \faLinkedin \hspace{0mm} \href{https://linkedin.com/in/massimocaruso}{\linkedin} $\vert$ 
    \faGithub \hspace{0mm} \href{https://github.com/Extinctable}{\github}
    }
\end{center}

\vspace{-8mm}


% Education Section
\section*{Education}
\vspace{-2mm}
\hrule
\vspace{0mm}

\textbf{Montreal, Canada} \hfill \textbf{Concordia University} \hfill \textbf{Jan 2023 -- Present} 
\vspace{-4mm}
\begin{itemize}[left=0.15in, itemsep=0pt]
    \item \textbf{Major:} Software Engineering, BEng
    \item \textbf{Relevant Courses:} Data Structures and Algorithms, Operating Systems, Databases, Embedded Systems, Machine Learning, and Deep Learning
\end{itemize}


% Experience Section
\vspace{-6mm} % Section separation
\section*{Experience}
\vspace{-2mm}
\hrule
\vspace{0mm}

{\href{https://www.payfacto.com}{\textbf{PayFacto - Payment Technology Solutions}}} \hfill \textbf{May 2025 -- August 2025} \\
{Software Implementation, Intern }
\vspace{-3mm}
\begin{itemize}[left=0.15in, itemsep=0pt]
    \item Spearheaded data acquisition, cleaning, and preprocessing of raw merchant data sets for the deployment of MEVWeb, a province-wide cloud-based SaaS platform mandated by Revenu Québec.
    \item Participated in end-to-end deployment of MEVWeb software remotely and on-site, including planning, testing, and installation.
    \item Supported hardware transitions by uninstalling legacy MEV devices and installing MEVWeb-compatible components such as printers and routers.
    \item Collaborated with project delivery, field services, and sales teams to ensure seamless coordination of deployments and merchant onboarding.
    \item Tested MEVWeb software builds and deployment packages, reporting bugs and verifying stability before production rollout.
\end{itemize}

{\href{https://www.athackctf.com}{\textbf{AtHackCTF}}} \hfill \textbf{Nov 2024 -- March 2025} \\
{Challenge Designer and Developer, Permanent Part-time}
\vspace{-3mm}

\begin{itemize}[left=0.15in, itemsep=0pt]
    \item Designed a complex RFID-based Capture the Flag (CTF) challenge using a real ATM machine and MIFARE Classic cards, which communicated with the machine's reader to simulate a security environment.
    \item Developed three flags requiring participants to:
    
        \begin{itemize}[left=0.2in, itemsep=0pt]
            \vspace{-2mm}
            \item Extract the card’s PIN from memory by reverse-engineering the RFID data.
            \item Manipulate the card's balance data, allowing the participant to alter the funds stored on the card.
            \item Modify the card's UID to impersonate an admin and escalate privileges within the system.
        \end{itemize}
        \vspace{-2mm}
    
    \item Implemented an interactive ATM interface, including buttons for navigation and a printer to issue flags upon successful completion of challenges.
    \item Facilitated the learning of hardware security, from memory manipulation to privilege escalation, within a real-world context.
    \item Prepared over 600 MIFARE Classic cards by writing custom data to each card and ensuring proper labeling and formatting for participant use.

\end{itemize}


% Projects Section
\vspace{-6mm}
\section*{Projects}
\vspace{-2mm}
\hrule
\vspace{0mm}

\textbf{Market Predictability (Deep Learning Project)}
\vspace{-4mm}
\begin{itemize}[left=0.15in, itemsep=0pt, label=--]
    \item Designed and implemented a PyTorch LSTM-based trading model to learn daily market leverage allocations on the Hull Tactical Market Prediction dataset, achieving an adjusted Sharpe score of \textbf{1.94}, indicating strong risk-adjusted performance with nearly twice as much return per unit of risk.
    \item Led systematic hyperparameter optimization across sequence length, hidden dimensions, learning rate, and regularization, identifying an optimal configuration that produced a cumulative strategy return of \textbf{122.4\%} versus \textbf{116.7\%} for a market benchmark.
    \item Developed evaluation and visualization pipelines to analyze equity curves, drawdowns, and rolling risk metrics, observing an average rolling Sharpe of approximately \textbf{1.14} with a maximum drawdown of \textbf{-25.2\%}.
\end{itemize}

\textbf{Embedded Wireless Access Control System}
\vspace{-4mm}
\begin{itemize}[left=0.15in, itemsep=1pt, label=--]
    \item Designed a two-node embedded access control system using ESP32 with BLE and LoRa, implementing servo-based lock actuation, tamper detection via analog sensing, and a deterministic finite state machine (armed, alarm, 2FA, disarmed) in C++ using PlatformIO.
    \item Implemented application-layer AES-128 encrypted alert messaging over LoRa and a BLE-based two-factor challenge--response protocol for local disarm, alongside an authenticated admin console with lockout policy and simulated biometric verification.
    \item Integrated multi-sensor inputs (potentiometer door position, IR motion, touch-based biometric) with encrypted wireless alerts, real-time console monitoring, and modular firmware architecture supporting offline simulation and incremental security hardening.
\end{itemize}

\textbf{Food Database System}
\vspace{-4mm}
\begin{itemize}[left=0.15in, itemsep=0pt, label=--]
    \item Developed an online nutritional database integrating APIs (FatSecret, TheMealDB) to provide detailed nutritional data, recipes, and dietary metadata.
    \item Cleaned and validated JSON data, storing in hybrid databases (PostgreSQL + MongoDB) with optimized queries, indexing, and aggregates.
    \item Automated data migration between SQL and NoSQL, improving retrieval efficiency with custom recipe-name generator for FatSecret API.
\end{itemize}

\textbf{Linear Regression Model}
\vspace{-4mm}
\begin{itemize}[left=0.15in, itemsep=0pt, label=--]
    \item Built a multiple regression model to analyze life expectancy factors (WHO dataset, 193 countries, 2000–2015).
    \item Applied backward elimination to reduce predictors from 20 to 6, achieving adjusted $R^2 = 0.77$ and predicting Canada’s 2013 life expectancy within 0.5 years of reported value.
    \item Used Python (Pandas, NumPy, Scikit-learn) for preprocessing, modeling, and visualization.
\end{itemize}


% Skills Section
\vspace{-6mm} % Section separation
\section*{Skills}
\vspace{-2mm}
\hrule
\vspace{0mm}
\textbf{Languages:} (Proficient): C, Java, LaTeX, HTML/CSS, Javascript, Python, SQL; (Familiar): C++, Clojure, Erlang \\
\textbf{Frameworks:} React, Node.js, Express.js, Flask, psycopg, Arduino, TensorFlow \\
\textbf{Libraries:} Pandas, NumPy, Matplotlib, Scikit-learn, PyTorch \\
\textbf{Developer Tools:} Git, Docker, Makefile, MongoDB, PostgreSQL, Neo4j, VS Code, Eclipse, Jupyter NB, PlatformIO \\
\textbf{Methodologies:} Agile development, Scrum, Waterfall

\end{document}
