\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[b4paper]{geometry}
\geometry{margin=0.5in}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

% Commands for my Contact Information
\newcommand{\fullname}{Massimo Caruso}
\newcommand{\phone}{(514) 944-5977}
\newcommand{\email}{massimo02caruso@gmail.com}
\newcommand{\linkedin}{linkedin.com/in/massimocaruso}
\newcommand{\github}{github.com/Extinctable}

% Commands for Recipient Information
\newcommand*{\hiringManager}{Miriam Diallo}
\newcommand*{\company}{CAE Inc.}
\newcommand*{\address}{8585 De la Côte-de-Liesse Rd, Saint-Laurent, Quebec H4T 1G5}

%Commands for the Body Paragraphs
\newcommand*{\position}{Software Engineering Intern}


% Name and Contact Information
\begin{center}
    {\Huge \textbf{\fullname}} \\
    \vspace{1mm}
    {\small 
    \faPhone \hspace{0mm} \href{tel:+15149445977}{\phone} $\vert$ 
    \faEnvelope \hspace{0mm} \href{mailto:massimo02caruso@gmail.com}{\email} $\vert$ 
    \faLinkedin \hspace{0mm} \href{https://linkedin.com/in/massimocaruso}{\linkedin} $\vert$ 
    \faGithub \hspace{0mm} \href{https://github.com/Extinctable}{\github}
    }
\end{center}


% Recipient Information
\vspace{1.5em}
\hiringManager \hfill \today \\
\company \\
\address 


% Opening
\vspace{1.5em}
Dear \hiringManager,

I am thrilled to apply for the \position \space role at \company \space As a Software Engineering student at Concordia University, I bring a robust foundation in software development, coupled with hands-on experience from academic and professional projects.

% Body
Throughout my position as a CTF Challenge Designer at AtHackCTF, I developed RFID-based Capture the Flag challenges to simulate real-world security scenarios. This experience enhanced my technical skills in system analysis, hardware/software integration, and designing interactive problem-solving environments—skills that directly align with the requirements of the \position \space role.

In addition, my academic projects, such as creating an online Food Database System and a Teacher-Student Feedback Web Application, allowed me to refine my expertise in Python, JavaScript, and SQL while working with APIs and relational databases. These projects taught me to manage end-to-end software development, optimize system performance, and focus on user-centered design.

% Why This Company
What excites me most about \company \space is its leadership in designing and deploying advanced defense and security systems that protect lives and ensure mission success. I am particularly drawn to the opportunity to contribute to developing innovative simulation technologies and scalable solutions for defense applications, which aligns with my career goals of advancing security and technology in high-stakes environments.

% Closing
I am confident that my technical skills, academic achievements, and passion for software engineering make me a strong candidate for the \position \space role. I would welcome the opportunity to discuss how my experiences align with the needs of your team. Please feel free to reach out to me at \phone \space or \href{mailto:massimo02caruso@gmail.com}{\email}.

\vspace{1.5em}
Thank you for considering my application. I look forward to the possibility of contributing to \company's success.

% Signoff
\vspace{2em}
Sincerely, \\
\fullname

\end{document}
